---
title: "Sample Marketing Report"
runtime: shiny
output: html_document
---


## (Company Name Here) Uplift and Campaign Report

### Global Performance

The following lists performence by global control groups and experimental groups. 

```{r, echo=FALSE}
library(dplyr,quietly = T,warn.conflicts = F)
library(shiny,quietly = T,warn.conflicts = F)
library(lubridate,quietly = T,warn.conflicts = F)
library(ggplot2,quietly = T,warn.conflicts = F)

```

```{r echo=FALSE}

inputPanel(
  sliderInput('numUserSegments',label = 'Number of User Segments', min = 1, max = 10, value = 5),
  sliderInput('numOffers',label = 'Number of Offers Trialed', min = 1, max = 10, value = 3),
  dateInput('dateStart', label = 'Date Start',value = Sys.Date()-15),
  dateInput('dateStop', label='Date End', value=Sys.Date())
  )
data = reactive({
  #days = ymd(seq(from=Sys.Date()-15, to=Sys.Date(), by="1 day"))
  days = seq(from=input$dateStart, to=input$dateStop, by="1 day")
  
  data = data.frame(segment=1, offer=1, day=days[1], performance=rexp(1), group="na") 
  perfmeans = runif(input$numOffers, min = 0.1, max = .5)
  for(g in c("control","experiment")){
    for(i in 1:input$numUserSegments){
      for(j in 1:input$numOffers){
        data = rbind(data, data.frame(segment=i, offer=j, day=days, performance=rexp(length(days), perfmeans[j]), group=g))
      }
    }
  }

  return(data[-1,])
})


renderDataTable({
   dataCtl = subset(data(), group=="control") %.%
    group_by(group) %.%
    summarize(performance=sum(performance),
              confLow=quantile(performance, .05),
              confHigh=quantile(performance, .95))
  
  dataOpt = data() %.%
    group_by(group) %.%
    summarize(performance=sum(performance),
              confLow=quantile(performance, .05),
              confHigh=quantile(performance, .95)) %.%
    mutate(percentUplift=round((performance-dataCtl$performance) / dataCtl$performance *100, digits=2),
           significant=ifelse(dataCtl$confHigh>confLow, "No", "Yes"))
  
  return(dataOpt)
})

renderPlot({
  dataCtl = subset(data(), group=="control") %.%
    group_by(day) %.%
    summarize(performance=sum(performance),
              confLow=quantile(performance, .05),
              confHigh=quantile(performance, .95))
  
  dataOpt = subset(data(), group=="experiment") %.%
    group_by(day) %.%
    summarize(performance=sum(performance),
              confLow=quantile(performance, .05),
              confHigh=quantile(performance, .95)) %.%
    mutate(uplift=round((performance-dataCtl$performance) / dataCtl$performance *100, digits=2)
           )
  
    ggplot(dataOpt, aes(x=day, y=uplift))+geom_line()+
    geom_hline(yintercept=0)+
    labs(title="Uplift by Day", y="%Uplift")
  
})

```

### Performance by Offer

The following table and charts list performance by Offer (across all experimental segments).


```{r echo=FALSE}
renderDataTable({
   dataCtl = subset(data(), group=="control") %.%
    group_by(group) %.%
    summarize(performance=mean(performance),
              confLow=quantile(performance, .05),
              confHigh=quantile(performance, .95))
  
  dataOpt = subset(data(), group="experiment") %.%
    group_by(offer) %.%
    summarize(performance=mean(performance),
              confLow=quantile(performance, .05),
              confHigh=quantile(performance, .95)) %.%
    mutate(percentUplift=round((performance-dataCtl$performance) / dataCtl$performance *100, digits=2),
           significant=ifelse(dataCtl$confHigh>confLow, "No", "Yes"))
  
  return(dataOpt)
})

renderPlot({
  dataCtl = subset(data(), group=="control") %.%
    group_by(day) %.%
    summarize(performance=mean(performance),
              confLow=quantile(performance, .05),
              confHigh=quantile(performance, .95))
  
  dataOpt = subset(data(), group=="experiment") %.%
    group_by(offer, day) %.%
    summarize(performance=mean(performance),
              confLow=quantile(performance, .05),
              confHigh=quantile(performance, .95)) %.%
    group_by(offer) %.%
    mutate(uplift=round((performance-dataCtl$performance) / dataCtl$performance *100, digits=2)
           )
  
    ggplot(dataOpt, aes(x=day, y=uplift, color=as.factor(offer)))+geom_line()+
    geom_hline(yintercept=0)+
    labs(title="Uplift by Day by Offer", y="%Uplift")
  
})

```


### Performance by Segment

The following table and charts list performance by Offer (across all experimental segments).

```{r echo=FALSE}
renderDataTable({
   dataCtl = subset(data(), group=="control") %.%
    group_by(group) %.%
    summarize(performance=mean(performance),
              confLow=quantile(performance, .05),
              confHigh=quantile(performance, .95))
  
  dataOpt = subset(data(), group="experiment") %.%
    group_by(segment) %.%
    summarize(performance=mean(performance),
              confLow=quantile(performance, .05),
              confHigh=quantile(performance, .95)) %.%
    mutate(percentUplift=round((performance-dataCtl$performance) / dataCtl$performance *100, digits=2),
           significant=ifelse(dataCtl$confHigh>confLow, "No", "Yes"))
  
  return(dataOpt)
})

renderPlot({
  dataCtl = subset(data(), group=="control") %.%
    group_by(day) %.%
    summarize(performance=mean(performance),
              confLow=quantile(performance, .05),
              confHigh=quantile(performance, .95))
  
  dataOpt = subset(data(), group=="experiment") %.%
    group_by(segment, day) %.%
    summarize(performance=sum(performance),
              confLow=quantile(performance, .05),
              confHigh=quantile(performance, .95)) %.%
    group_by(segment) %.%
    mutate(uplift=round((performance-dataCtl$performance) / dataCtl$performance *100, digits=2)
           )
  
    ggplot(dataOpt, aes(x=day, y=uplift, color=as.factor(segment)))+geom_line()+
    geom_hline(yintercept=0)+
    labs(title="Uplift by Day by Segment", y="%Uplift")
  
})

```




### Peformance by User Segment-Offer Pairs

```{r echo=FALSE}
renderDataTable({
   dataCtl = subset(data(), group=="control") %.%
    group_by(group) %.%
    summarize(performance=mean(performance),
              confLow=quantile(performance, .05),
              confHigh=quantile(performance, .95))
  
  dataOpt = subset(data(), group="experiment") %.%
    group_by(offer, segment) %.%
    summarize(performance=mean(performance),
              confLow=quantile(performance, .05),
              confHigh=quantile(performance, .95)) %.%
    mutate(percentUplift=round((performance-dataCtl$performance) / dataCtl$performance *100, digits=2),
           significant=ifelse(runif(input$numUserSegments)<.5, "No", "Yes"))
  
  return(dataOpt)
})

renderPlot({
  dataCtl = subset(data(), group=="control") %.%
    group_by(day) %.%
    summarize(performance=mean(performance),
              confLow=quantile(performance, .05),
              confHigh=quantile(performance, .95))
  
  dataOpt = subset(data(), group=="experiment") %.%
    group_by(offer, segment, day) %.%
    summarize(performance=mean(performance),
              confLow=quantile(performance, .05),
              confHigh=quantile(performance, .95)) %.%
    group_by(offer, segment) %.%
    mutate(uplift=round((performance-dataCtl$performance) / dataCtl$performance *100, digits=2)
           )
  
  dataOpt[["segOffer"]] = paste(dataOpt$segment, dataOpt$offer, sep="")
    ggplot(dataOpt, aes(x=day, y=uplift, color=as.factor(segOffer)))+geom_line()+
    geom_hline(yintercept=0)+
    labs(title="Uplift by Day", y="%Uplift")
  
})

```



## Segment and Offer Composition

Here we list what the segments are composed of for a deeper dive into why the segment may or may not be working.

We also list what each of the offers is for the same reason:  figuring out why the offer may or may not be working.

## Conclusions and Analysis

Here is some custom explanatory text and some supplimental figures.  This explanatory text will point out what's going well with the campaigns and what isn't.  

